Probabilities of polar alignment in circumbinary disks

### 2024-12-17 src/tex/ms.tex
Mention the effects of j in the conclusion

Our results show that $f_\text{polar}$ is heavily dependent on the underlying parameter distributions that make up a population of systems. There are some populations (e.g. low mass disks around near-circular binaries) where we expect $f_\text{polar}$ to be near zero. Other populations (e.g. low mass disks orbiting binaries with a uniform distribution of $e_\text{b}$) where our results are consistent with previous results from \citet{ceppi2024} which found $f_\text{polar}\sim 0.5$.

>>>>

Our results show that $f_\text{polar}$ is heavily dependent on the underlying parameter distributions that make up a population of systems. There are some populations (e.g. low mass disks around near-circular binaries) where we expect $f_\text{polar}$ to be near zero. Other populations (e.g. low mass disks orbiting binaries with a uniform distribution of $e_\text{b}$) where our results are consistent with previous results from \citet{ceppi2024} which found $f_\text{polar}\sim 0.5$. When we look at disks with considerable mass, however, the effects of binary eccentricity are significantly weakened. A massive disk is capable of exciting Kozai-Lidov oscillations on the binary, changing its eccentricity and allowing polar orbits for much smaller (initial) values of $e_\text{b}$. We find a limit that $f_\text{polar}$ tends to as $j\rightarrow \infty$ which is dependent on the distribution of initial mutual inclination. Increasing $j$ moves $f_\text{polar}$ towards this limit.
